---
title: "Homework 1"
author: "Koji Takagi"
format: html
editor: visual
---

## What do you think being a data scientist is about?

Data science is about using data to find useful and meaningful insights.

In my job, I work mostly with clinical trial data. I focus on:
- Reading and cleaning raw data
- Running statistical analyses based on a pre-written Statistical Analysis Plan (SAP)
- Making clear tables and figures

I don’t usually choose the methods, but I know how to apply them correctly.  
I hope to grow in the future and be more involved in selecting the appropriate methods.

## What differences/similarities do you see between data scientists and statisticians?

- **Similarities:**
  - Both use data to make decisions.
  - Both rely on statistical models and programming tools.
- **Differences:**
  - Statisticians focus more on theory and study design.
  - Data scientists often work more with coding, automation, and production environments.

## How do you view yourself in relation to these two areas?

Currently, I work as a **data analyst**.

- I follow instructions from the SAP rather than designing the analysis myself.
- I am confident in using tools like R and SAS to produce reliable results.
- I care about accuracy, reproducibility, and clean code.
- I want to grow step-by-step toward statistical thinking and method selection.

---

## R Code: Exploring a Density Object

We will now create a density object based on the `Petal.Width` variable from the `iris` dataset.

The object `y` stores the result of the `density()` function, which calculates a kernel density estimate of the values.

Below, we check the **class**, **type**, and **structure** of the object `y`.

```{r}
#| echo: true

y <- density(iris$Petal.Width)

class(y)
typeof(y)
str(y)
```

```{r}
#| echo: false

plot(y)
```